\documentclass[12pt,a4paper,norsk]{article}

\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{framed}
\usepackage{color}
\usepackage[colorlinks]{hyperref}
\hypersetup{linkcolor=DarkRed}
\providecommand{\shadedwbar}{}
\definecolor{shadecolor}{rgb}{0.87843, 0.95686, 1.0}
\renewenvironment{shadedwbar}{
\def\FrameCommand{\color[rgb]{0.7,     0.95686, 1}\vrule width 1mm\normalcolor\colorbox{shadecolor}}\FrameRule0.6pt
\MakeFramed {\advance\hsize-2mm\FrameRestore}\vskip3mm}{\vskip0mm\endMakeFramed}
\providecommand{\shadedquoteBlueBar}{}
\renewenvironment{shadedquoteBlueBar}[1][]{
\bgroup\rmfamily
\fboxsep=0mm\relax
\begin{shadedwbar}
\list{}{\parsep=-2mm\parskip=0mm\topsep=0pt\leftmargin=2mm
\rightmargin=2\leftmargin\leftmargin=4pt\relax}
\item\relax}
{\endlist\end{shadedwbar}\egroup}


\title{Seminar 11 for Lecture 10}
\author{}
\date{\today}


\begin{document}
\maketitle
\noindent \section {Question 1:}Which of the following mobile devices is more like to be shared?\\

\begin{itemize}
 \item \textbf{a} \textit{ Smart phones}
 \item \textbf{b} \textit{ Tablets}
 \item \textbf{c} \textit{ Phablets}
 \item \textbf{d} \textit{ Personal Digital Assistans (PDAs)}
\end{itemize}

\underline {\textbf{Answer: b}}. Tablets\\
\indent \\ Thablets
\noindent Coments:\\
\framebox(450,100){}\\

\noindent \section{ Question 2:} Which of the following are typical behaviors for smartphones users?\\

\begin{itemize}
 \item \textbf{I)} \textit{They go to the mobiles when they want to "kill time" while waiting.}
 \item \textbf{II)} \textit{They are patient and understand the shortcommings of developing mobile technology.}
 \item \textbf{III)} \textit{They are rushed and most of the times, impatient.}
\end{itemize}

\begin{itemize}
 \item \textbf{a)} \textit{I, II}
 \item \textbf{b)} \textit{I, III}
 \item \textbf{c)} \textit{II, III}
 \item \textbf{d)} \textit{I, II, III}
\end{itemize}
\underline{\textbf{Answer: b}}. I, III\\

\noindent Coments:\\
\framebox(450,100){}\\

\section {Question 3:} Which of the following is a good advice for developing software for mobiles?\\

\begin{itemize}
 \item \textbf{a)} \textit{Create new many new gestures and fonts, so that your software stands-out in a competitive market.}
 \item \textbf{b)} \textit{Suport standard navigation ands gestures for users interacting with the mobile application you are developing.}
 \item \textbf{c)} \textit{Use early registartion, so that you can easily track all users who want to try your software.}
 \item \textbf{d)} \textit{Use a big background image with your company name instead of your company logo, so that you save display space.}
\end{itemize}

\underline{\textbf{Answer: b}} Suport standard navigation ands gestures for users interacting with the mobile application you are developing. \\

\noindent Coments:\\
\framebox(450,100){}\\

\section {Question 4:} Which of the following is a typical issue for software running on mobile devices?\\

\begin{itemize}
 \item \textbf{a)} \textit{Hard to keep track of software updates.}
 \item \textbf{b)} \textit{Low memory consumption}
 \item \textbf{c)} \textit{Accidental activation of certain features}
 \item \textbf{d)} \textit{Additional data traffic}


\end{itemize}

\underline{\textbf{Answer: c}} Accidental activation of certain features. \\

\noindent Coments:\\
\framebox(450,100){}\\

\section {Question 5: Open-end question} Which problems could you highlight related to the following sites?\\
\href{http://m.nbc.com/}{http://m.nbc.com/}\\
\href{http://m.ikea.com/}{http://m.nbc.com/}\\
\href{http://m.bestbuy.com/}{http://m.nbc.com/}\\


\noindent Coments:\\
\framebox(450,100){}\\


\end{document}